### 2021-11-18 README.Rmd
Updated documentation with errorplot example

The next example creates a line plot of vector `x` against the columns of matrix `y` by using `plot_type = "line"`. Although the lines would be represented using different colors by default, the `color` parameter allows custom colors to be assigned to them.
The following plot assigns custom colors to the lines, and the limits of the y axis are updated using the `ylim` parameter. Further, a ggplot theme is added on to the resultant ggplot object.

@@

It is also worth noticing that `alpha` isn't a parameter defined in `ggmatplot()`, but can be used. This is because `ggmatplot` is built upon `ggplot2`, and each `plot_type` corresponds to a [`geom`](https://ggplot2.tidyverse.org/reference/index.html#section-geoms). Therefore, all valid parameters with the underlying [`ggplot2 geom`](https://ggplot2.tidyverse.org/reference/index.html#section-geoms) can be used with `ggmatplot()`

@@

>>>>

The next example creates a line plot of vector `x` against the columns of matrix `y` by using `plot_type = "line"`. Although the lines would be represented using different colors by default, the `color` parameter allows custom colors to be assigned to them.

The following plot assigns custom colors to the lines, and the limits of the y axis are updated using the `ylim` parameter. Further, a ggplot theme is added on to the resultant ggplot object.

@@

It is also worth noticing that `alpha` isn't a parameter defined in `ggmatplot()`, but can be used. This is because `ggmatplot` is built upon `ggplot2`, and each `plot_type` corresponds to a [`geom`](https://ggplot2.tidyverse.org/reference/index.html#section-geoms) as listed [here](./reference/ggmatplot.html#plot-types). Therefore, all valid parameters with the underlying [`ggplot2 geom`](https://ggplot2.tidyverse.org/reference/index.html#section-geoms) can be used with `ggmatplot()`.

@@

Error plots also accept only a single matrix input, and plots out error bars for each column of the matrix. The `desc_stat` parameter of `ggmatplot()` can be used to define what the mid point and error bars of the plot should represent.

The next example, plots out an `errorplot` using the medians and interquartile ranges of each variable.

```{r errorplot}
# matrix x
x <- (iris[, 1:4])

ggmatplot(x,
  plot_type = "errorplot",
  desc_stat = "median_iqr",
  xlab = "Group",
  size = 1
) +
  theme_minimal()
```
